%-------------------------
% Resume in LaTeX
% Clean two-page layout
%-------------------------
\documentclass[10pt,a4paper]{article}

\usepackage[a4paper,left=0.48in,right=0.48in,top=0.38in,bottom=0.44in]{geometry}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\multicolsep}{2pt}
\setlength{\columnsep}{14pt}
\setlength{\footskip}{10pt}

%-------------------------
% Section formatting
\titleformat{\section}{
  \vspace{6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{3pt}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textbf{\small #2} \\
    \textit{\small #3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
    \small #1 & \textbf{\small #2} \\
  \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in,label={},itemsep=8pt,topsep=2pt,parsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.16in,itemsep=2pt,topsep=2pt,parsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{3pt}}
\newcommand{\achievementCategory}[1]{\vspace{7pt}\noindent\textbf{#1}\vspace{2pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

%-------------------------
% Document start
\begin{document}

%-----------HEADER-----------
\begin{center}
  {\Huge \scshape Sanjay Gandhi} \\
  \vspace{3pt}
  \small Phone: +91-8847472124 $|$
  \href{mailto:sanjaymaheshwari.work@gmail.com}{Email: sanjaymaheshwari.work@gmail.com} \\
  \small \href{https://linkedin.com/in/snjumaheshwari}{LinkedIn: linkedin.com/in/snjumaheshwari} $|$
  \href{https://portfolio-sanjay-tech.vercel.app/}{Web: portfolio-sanjay-tech.vercel.app}
\end{center}
\vspace{-2pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\noindent\small{\textbf{Senior Software Engineer and Tech Lead} with \textbf{6+ years} of experience building and scaling backend and distributed systems at \textbf{Oracle, Google, and Amazon}. Leadership experience across \textbf{10+ engineers}, \textbf{3+ products}, and \textbf{7+ microservices}. Recognized as a \textbf{Certified Bar Raiser at Oracle}. Expertise in cloud-native systems across \textbf{Healthcare, Search, and Finance}, with strong skills in \textbf{Java, Python, OCI, AWS, distributed systems, and asynchronous architectures}. Applied \textbf{Machine Learning and Generative AI} to report intelligence, developer productivity, and anomaly detection.}
\vspace{4pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Oracle}{Apr 2024 -- Present}
    {Senior Member of Technical Staff (SDE III) -- \textbf{Promoted to Tech Lead (Oct 2025)}}{Bengaluru (Remote)}
  \resumeItemListStart
    \resumeItem{Own architecture, technical direction, delivery, and production readiness for Oracle Health's \textbf{MRO / Clinical Reporting Gen2} platform across \textbf{3+ products}.}
    \resumeItem{Architected and implemented \textbf{7+ Java Micronaut microservices}, evolving the platform into modular APIs for template management, data extraction, report generation, and the \textbf{PDF Output Assembler}.}
    \resumeItem{Led product delivery across \textbf{4 quarterly releases}, translating roadmaps into scoped work for \textbf{5--8 engineers}, unblocking execution, and driving architecture, defect resolution, compliance, monitoring, and production readiness.}
    \resumeItem{Resolved a critical production issue where approximately \textbf{1,000-page reports} breached the \textbf{30-second SLA}; reduced heap usage by \textbf{40\%}, improved performance by over \textbf{25\%}, and drove request-level caching that cut data-extraction time by \textbf{60\%}.}
    \resumeItem{Built the cloud-native platform with \textbf{Java, Micronaut, React, Large Semantic Object Storage, and Oracle Cloud Infrastructure}; added Kafka-based async processing, retries, DLQs, idempotency, horizontal scaling, dashboards, metrics, and alerting.}
    \resumeItem{Partnered with \textbf{25+ cross-functional teams} to turn custom clinical-reporting needs into scalable platform capabilities and reduced Gen2 onboarding from roughly \textbf{2 weeks to under 1 week}.}
    \resumeItem{Led a project involving \textbf{3 engineers} to deliver Gen1 \textbf{Report Ingress} and \textbf{6 APIs} in \textbf{1 quarter + 1 month} vs. \textbf{2 quarters planned}; enabled WebSphere-to-EJS migration with better performance, stability, scalability, and lower cost.}
    \resumeItem{Resolved technical and scope ambiguities across multiple initiatives and contributed to early-stage architecture and planning for the \textbf{SI DRZ region build} and \textbf{EHRC modernization program}.}
    \resumeItem{Built and led the India Clinical Reporting team from scratch, with leadership scope across \textbf{10+ engineers}; strengthened hiring through \textbf{100+ interviews} and \textbf{25+ hires}.}
  \resumeItemListEnd

  \resumeSubheading
    {Google}{Sep 2021 -- Feb 2024}
    {Software Engineer II}{Bengaluru (Hybrid)}
  \resumeItemListStart
    \resumeItem{Worked in the \textbf{Search India} team, developing education-domain features for exam OSRPs to deliver structured educational content.}
    \resumeItem{Built the \textbf{Exam Quiz} feature to improve user engagement with interactive learning modules.}
    \resumeItem{Migrated architecture from entity-driven to intent-driven, impacting \textbf{0.05\%} of Search traffic.}
    \resumeItem{Launched localized \textbf{Exam OSRP} experiences with tabs and content in Hindi, Tamil, and Telugu to improve accessibility.}
    \resumeItem{Designed and integrated a scalable \textbf{Language API} for Indic locales in lower-tier cities.}
    \resumeItem{Collaborated with cross-functional teams to resolve issues, align requirements, and prioritize enhancements.}
    \resumeItem{Worked on a large-scale \textbf{monorepo codebase} involving \textbf{C++, Java, Python, gRPC, protobuf, and Graph Database (Knowledge Graph)}, alongside internal technologies.}
  \resumeItemListEnd

  \resumeSubheading
    {Amazon}{Jul 2020 -- Aug 2021}
    {Software Development Engineer I}{Hyderabad}
  \resumeItemListStart
    \resumeItem{Worked in \textbf{Amazon Finance Automation}, building statistical and ML-powered systems to detect invoice fraud, duplicates, and anomalies at scale.}
    \resumeItem{Implemented \textbf{3} ML-based anomaly-detection rules using \textbf{Isolation Forest}, identifying over \textbf{100M USD} in anomalies.}
    \resumeItem{Reduced anomaly reporting latency from \textbf{24 hours} to near real-time through \textbf{Gandalf-Veritas Integration}.}
    \resumeItem{Built APIs and monitoring dashboards, and used \textbf{AWS CDK} to create infrastructure and CI/CD pipelines.}
    \resumeItem{Developed microservices using \textbf{Java, Kotlin, TypeScript, Python, ML, Elasticsearch, DynamoDB, and Redshift}, alongside Coral, Smithy, and AWS technologies.}
  \resumeItemListEnd

  \resumeSubheading
    {HackerEarth}{Jan 2020 -- Jun 2020}
    {Problem Curator Intern}{Bengaluru}
  \resumeItemListStart
    \resumeItem{Created and tested algorithmic problems for hiring contests at companies including Infosys, Google, Facebook, Nokia, PayPal, and Salesforce.}
    \resumeItem{Presented a \textbf{2-day / 10+ hour} Advanced Data Structures and Algorithms workshop at MNIT Jaipur to \textbf{120+} attendees on behalf of HackerEarth.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\newpage

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Lovely Professional University}{Jul 2016 -- May 2020}
    {B.Tech. in Computer Science Engineering, Specialization: Machine Learning}{Jalandhar, Punjab | \href{https://drive.google.com/file/d/1n-Xg5Bm-tyqGOUC7onOlteQrPqXydC8Z/view}{\underline{CGPA: \textbf{9.06/10}}}}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\vspace{2pt}
\begin{tabular}{p{0.22\textwidth} p{0.74\textwidth}}
  \textbf{Languages} & Java, C++, Python, TypeScript \\
  \textbf{Databases} & MySQL, DynamoDB, MongoDB, Redshift, Object Storage \\
  \textbf{Cloud \& Infra} & AWS, OCI, Docker, Kubernetes, CI/CD, Terraform/CDK \\
  \textbf{Distributed Systems} & Kafka, gRPC, Redis, Elasticsearch, Microservices, WebSockets \\
  \textbf{AI \& Machine Learning} & Scikit-Learn, Isolation Forest, Anomaly Detection, Gen AI, MCP Server, Agents\\
  \textbf{Miscellaneous} & System Design, API Design, Performance Tuning, Code Reviews, Mentoring, Documentation \\
\end{tabular}
\vspace{3pt}

%-----------ACHIEVEMENTS-----------
\section{Achievements}

\achievementCategory{Professional \& Leadership}
{\small
\begin{itemize}[leftmargin=0.30in,topsep=2pt]
  \item Promoted to \textbf{Tech Lead}, owning architecture, delivery, and technical direction for a multi-service healthcare platform with leadership experience across \textbf{10+ engineers}.
  \item Oracle Certified Bar Raiser; conducted \textbf{100+ interviews} and contributed to \textbf{25+ hires}. OraHacks judge and mentor for \textbf{10+ AI teams}, guiding projects from proof of concept toward production.
  \item First student from the university to receive a \textbf{direct SDE full-time offer from Amazon} during third-year on-campus internship hiring.
\end{itemize}
}

\achievementCategory{Cloud \& Technical Certifications}
{\small
\begin{itemize}[leftmargin=0.30in,topsep=2pt]
  \item \href{https://catalog-education.oracle.com/pls/certview/sharebadge?id=C72EFA41F0C8B51EEDCF7E759B92FCA34E59F058D11AFD39D71DB564ABB8DDFE}{Oracle Cloud Infrastructure 2025 Generative AI Professional}
  \item \href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=E6EA0D02CCCB8650680C392264F1F29B72C5B8895C915ED25C8F1C63C6D850EE}{Oracle Cloud Infrastructure 2025 Certified Developer Professional}
  \item \href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=0A80139CE66ACD03D6226677B4ED648AE55C308A559F9D9E222F1906F6DF6904}{Oracle Cloud Infrastructure 2024 Certified AI Foundations Associate}
  % \item \href{https://catalog-education.oracle.com/ords/certview/sharebadge?id=54658A707D70FAE955041F74C82458539E2EB6ACD5F2BBB5FAD88DAF8767FA12}{Oracle Cloud Infrastructure 2023 Certified Foundations Associate}
  \item \href{https://www.codechef.com/certificates/public/1765982}{CodeChef Certified Data Structures and Algorithms Programme \textbf{(CCDSAP -- Advanced)}}
  \item \href{https://www.linkedin.com/in/snjumaheshwari/details/certifications/}{Earned \textbf{30+ technical certifications} across computer science, cloud, and software engineering.}
\end{itemize}
}

\achievementCategory{Competitive Programming \& Coding Excellence}
{\small
\begin{itemize}[leftmargin=0.30in,topsep=2pt]
  \item Secured \textbf{World Rank 1} in CodeChef October Challenge 2018 (Div 2).
  \item Qualified for \textbf{ACM-ICPC Asia Regionals}; secured \textbf{85th} rank in Gwalior-Pune regionals, 2018.
  \item Secured \textbf{2nd} rank out of \textbf{175 teams} in University Coding Contest at LPU.
  \item Secured \textbf{5th} rank in the national coding contest ``ALOHOMORA'' at NIT Durgapur.
  \item Secured \textbf{21st} rank in a national coding contest at LNMIIT Jaipur.
  \item Solved \textbf{1000+} problems across major competitive programming platforms.
\end{itemize}
}

\achievementCategory{National Exams \& Academic Rankings}
{\small
\begin{itemize}[leftmargin=0.30in,topsep=2pt]
  \item Obtained \textbf{99.98 percentile} in eLitmus Quantitative Aptitude.
  \item Secured \textbf{86th} rank among \textbf{60,946} candidates in Rajasthan Pre-Engineering Test, 2014.
  \item Secured \textbf{15,550} rank among \textbf{1.26 lakh} candidates in JEE Advanced.
  \item Participated in \textbf{3 hackathons}, developing projects in machine learning and web development.
\end{itemize}
}
\vspace{2pt}

%-----------ONLINE PROFILES-----------
\section{Online Profiles}
\vspace{2pt}
\begin{multicols}{4}
\begin{itemize}[leftmargin=*,itemsep=3pt,topsep=0pt,label={}]
  \item[] \href{https://github.com/Maheshwari-Tech}{\underline{Github}}
  \item[] \href{https://leetcode.com/u/snjumaheshwari/}{\underline{Leetcode}} \\
    \small{Rating: 1811* \textbf{top 10\%}}
  \item[] \href{https://codeforces.com/profile/snjumaheshwari98}{\underline{Codeforces}} \\
    \small{Rating: 1813* \textbf{Expert}}
  \item[] \href{https://www.codechef.com/users/snjumaheshwari}{\underline{CodeChef}} \\
    \small{Rating: 2022* \textbf{5-Star}}
\end{itemize}
\end{multicols}


%-----------PERSONAL PROJECTS-----------
\section{Personal Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\href{https://portfolio-sanjay-tech.vercel.app/}{\textbf{Portfolio Website}} $|$ \href{https://portfolio-sanjay-tech.vercel.app/}{\underline{Live}} $|$ \emph{Next.js, TypeScript, FastAPI, Supabase, Vercel, AWS Cloud}}{2025 -- Present}
  \resumeItemListStart
    \resumeItem{Built a production-oriented portfolio with searchable blogs, detailed project case studies, certificate previews, role-based member/admin experiences, and a separately deployable FastAPI backend.}
    \resumeItem{\textbf{Intelligent Report Builder:} AI workspace for report requests, templates, quality review, and SLA prediction.}
    \resumeItem{\textbf{LLM Semantic Query Agent:} Validated NL-to-SQL with pgvector retrieval and \textbf{90\% lower prompt-token cost}.}
    \resumeItem{\textbf{Agentic AI Support:} LangGraph/RAG agent using MCP tools over support documents and governed APIs.}
    \resumeItem{\textbf{Cards Game:} Reconnect-safe multiplayer Indian card games across web and mobile.}
    \resumeItem{\textbf{Udhari:} Chat-first peer lending with versioned terms, AutoPay, and repayment tracking.}
    \resumeItem{\textbf{CouplesCraft:} Location-aware date planning with budget ranking, maps, and shared memories.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
